### 2025-03-04 sports-cognitive-psychology.qmd
20250301 - hot hand fallacy
20250304 - cites

## Other Coaching Absurdities {#sec-coachingAbsurdities}

@@

However, does icing the kicker work?
There is mixed evidence on icing the kicker.
Some studies find some evidence for lower percentage of iced kicks made compared to non-iced kicks [@Goldschmied2024], whereas other studies do not [e.g., @GonzalezSanchez2024; @Moskowitz2011].
This suggests that, if there is such an effect, the [effect size](#sec-practicalSignificance) is likely very small, and it may better suit the team to use your timeouts in other situations.

>>>>

## Other Beliefs in Sports {#sec-beliefsInSports}

@@

However, does icing the kicker work?
There is mixed evidence on icing the kicker.
Some studies find some evidence for lower percentage of iced kicks made compared to non-iced kicks [@Goldschmied2024], whereas other studies do not [e.g., @Berry2004; @GonzalezSanchez2024; @Moskowitz2011].
This suggests that, if there is such an effect, the [effect size](#sec-practicalSignificance) is likely very small, and it may better suit the team to use your timeouts in other situations.

### Hot Hand {#sec-hotHand}

The belief in the "hot hand" is described in @sec-fallaciesHotHand.
